Supplementary material for \\Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-05-05 paper/ifo-complexAudio.tex
adding references to signal processing textbooks from Changrong

Here we use the Michelson interferometer as an ``optical microphone'', where a laser is used to detect sound instead of the electrical components in a conventional microphone.
Optical microphones have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defense industry and operate on a variety of related principles. We use the term ``optical microphone'' to distinguish this technology from those previous technologies.
Our objective is to play a recording of speech or music through the speaker attached to mirror M2 (see Fig.~\ref{fig:ifo_schematic_webcam}), record the resulting interference pattern, and then recover the original signal via a selection of signal processing techniques.

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. 
Instead, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
A selection of filters is applied to the data, details of which are presented in Supplementary Material. 
We present the two best-performing analyses from our Supplementary Material in Section~\ref{sec:opticalMicResults}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/combined_highlight_results_melatos_labelled.pdf}
\caption{\label{fig:notchWienerLogMMSEResults}
Timeseries (left column) and frequency spectrum (right column) results with the optical microphone. 
The original input signal in the first row is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode''). 
 The input signal is shifted by 0.12 s to the right to synchronize the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
The second row shows the raw output from the optical microphone when the input from the first row is played. 
The third row shows the result of applying the notch and Wiener filter combined. 
The fourth row shows the result of applying the logMMSE estimator, where the rise at the start of the timeseries is an expected effect when filtering a signal of finite duration. 
}
\end{center}
\end{figure*}

>>>>

Here we use the Michelson interferometer as an ``optical microphone'', where a laser is used to detect sound instead of the electrical components in a conventional microphone.
Optical microphones have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defense industry and operate on a variety of related principles. 
%We use the term ``optical microphone'' to distinguish this technology from those previous technologies.
Our objective is to play a recording of speech or music through the speaker attached to mirror M2 (see Fig.~\ref{fig:ifo_schematic_webcam}), record the resulting interference pattern, and then recover the original signal via a selection of signal processing techniques.

This analysis is indirectly related to the advanced signal processing techniques required to extract gravitational-wave signals. 
Instead, the apparatus serves as an independent demonstration for a broader physics and engineering audience, particularly in undergraduate laboratories. 
We describe additional hardware components required for this demonstration in Section~\ref{sec:photodiode} and the initial results in Section~\ref{sec:initialResultsOpMic}. 
A selection of filters is applied to the data, details of which are presented in Supplementary Material. 
For introductory information on digital signal processing, we refer the reader to a selection of textbooks~\cite{Mitra:2011, Lyons:2011, Stein:2000, OpenheimSchaferBuck:1999, PrakisManolakis:1996,10.5555/151045}. 
In Section~\ref{sec:opticalMicResults} we present the two best-performing analyses from our Supplementary Material.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{figures/combined_highlight_results_melatos_labelled.pdf}
\caption{\label{fig:notchWienerLogMMSEResults}
Timeseries (left column) and frequency spectrum (right column) results with the optical microphone. 
The original input signal in the first row is a $1\,{\rm s}$ recording of an adult male voice (saying ``A cathode''). 
 The input signal is shifted by 0.12 s to the right to synchronize the manual delay from starting the recording with the Raspberry Pi and starting to play the source through the speaker. 
The second row shows the raw output from the optical microphone when the input from the first row is played. 
The third row shows the result of applying the notch and Wiener filter combined. 
The fourth row shows the result of applying the logMMSE estimator, where the rise at the start of the timeseries is an expected effect when filtering a signal of finite duration. 
}
\end{center}
\end{figure*}
